### 2013-07-07 paper.tex
Added some more to discussion

\section{Discussion}
\subsection{Error tolerance}
As seen in table \ref{heights} either when the vertical tilt angle is very wide, standing close to the tree, or very narrow, standing far away, leads to error. It's not clear what is causing this but there a two possibl reasons. The first one is that because of the short focal length of the camera and overall poor quality when compared to a real camera, causes various forms of distrotion, especially around the edges of the image. When the person is standing close to the tree so the vertical tilt angle is over 45\degree, the points tend to lie exactly there, around the edges of the image. The distortion then affects these points causing the pixel measurements to be incorrect. The other problem occurs in the direct opposite situation, when the person is standing far away and the angle is very narrow. Naturally what happens is that the resolution of the camera just isn't high enough and the pixel measurements just aren't accurate anymore. However most of this distortion seems to only affect the vertical measurements because when looking at table \ref{widths} it is clearly seen that the readings do not stray much at all from their actual values. Despite this the deviation in the height readings still alters the volume calculations. Ideally a person should stand so that the vertical tilt angle lies between 45\degree and 25\degree which is basically means they should stand somewhere between one tree length to two tree length's from the tree.
\subsection{Limitations}
As pointed out in the previous section the main hindrance attatched to this application is the actual camera. 
\subsection{Future development}
The main area that could be expanded on is the edge detection. As explained in the background, today computer vision is still far from perfect. However that will hopefully change in the near future and things like Mechanical Turk can be dropped for a more efficient system that produces little to no error and works autonomously.

>>>>

\section{Discussion}
\subsection{Error tolerance}
As seen in table \ref{heights} either when the vertical tilt angle is very wide, standing close to the tree, or very narrow, standing far away, leads to error. It's not clear what is causing this but there a two possibl reasons. The first one is that because of the short focal length of the camera and overall poor quality when compared to a real camera, causes various forms of distrotion, especially around the edges of the image. When the person is standing close to the tree so the vertical tilt angle is over 45\degree, the points tend to lie exactly there, around the edges of the image. The distortion then affects these points causing the pixel measurements to be incorrect. The other problem occurs in the direct opposite situation, when the person is standing far away and the angle is very narrow. Naturally what happens is that the resolution of the camera just isn't high enough and the pixel measurements just aren't accurate anymore. However most of this distortion seems to only affect the vertical measurements because when looking at table \ref{widths} it is clearly seen that the readings do not stray much at all from their actual values. Despite this the deviation in the height readings still alters the volume calculations. Ideally a person should stand so that the vertical tilt angle lies between 45\degree and 25\degree which is basically means they should stand somewhere between one tree length to two tree length's from the tree.
\subsection{Limitations}
As pointed out in the previous section the main hindrance attatched to this application is the actual camera. The problem is that most mobile phone cameras have a lot of different distortions that make it hard to make accurate measurements. Also when the tree is far away, the resolution of the camera can have a large affect on the final result. Human error is still large factor. If the person is not holding the phone properly, takes a blurry photo or in any other way alters the image, will cause the calculations to be incorrect. Mechanical Turk is also a weak link because it is essentially humans doing the work and there nothing stopping them from also making mistakes. 
\subsection{Future development}
The main area that could be expanded on is the edge detection. As explained in the background, today computer vision is still far from perfect. However that will hopefully change in the near future and things like Mechanical Turk can be dropped for a more efficient system that produces little to no error and works autonomously. If camera technology in mobile phones doesn't improve then being able to correct the various distortions would also make an improvement. The possibilty might also be there in the future to have the application calculate extra things like canopy area and even adding in the volume of external branches to the main volume.
